Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Remove todo item on TSR effects
Text wrapping
Add info about McTavish et al (2013); resolves #26

\todo[inline]{Kinematic scaling effects? Matching TSR?}

@@

The performance and wake characteristics of cross-flow (vertical axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag and operational parameters such as tip speed ratio---{\em
    and} on Reynolds number. Note that an average blade chord Reynolds number,
$Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be expressed in terms
of tip speed ratio $\lambda \equiv \omega R/ U_\infty$; the value of $\lambda$
at which a turbine reaches peak performance is again a function of turbine
solidity $Nc/\pi D$.

@@

Krogstad and Adaramola observed Reynolds number independence of the performance for a 0.9 m
diameter axial-flow turbine rotor at $Re_D \approx 5 \times 10^5$ in wind tunnel
tests \cite{Krogstad2012a}. Their turbine blades had an S826 profile along their entire span, a profile chosen for its $Re$-independence. Walker et al. \cite{Walker2014} similarly chose a NACA 63-618 foil for their axial-flow turbine tests in a towing tank, which were performed at a mid span Reynolds number $Re_c = 4 \times 10^5$.

\todo[inline]{bring back the examples of studies at small scale? (too small)}

@@

Previously, is has been observed experimentally that a cross-flow turbine wake's
unique vortical mean flow field is responsible for accelerated wake recovery
when compared with conventional axial-flow propeller-type turbines
\cite{Bachant2015-JoT}. In this study we seek to replicate the same energy
balance considerations at multiple Reynolds numbers, to examine the implications
on how small scale, i.e. low Reynolds number experiments may be used to study
flows in turbine arrays.

>>>>

@@

The performance and wake characteristics of cross-flow (vertical-axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag and operational parameters such as tip speed ratio---{\em
    and} on Reynolds number. Note that an average blade chord Reynolds number,
$Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be expressed in terms
of tip speed ratio $\lambda \equiv \omega R/ U_\infty$; the value of $\lambda$
at which a turbine reaches peak performance is again a function of turbine
solidity $Nc/\pi D$.

@@

Krogstad and Adaramola observed Reynolds number independence of the performance
for a 0.9 m diameter axial-flow turbine rotor at $Re_D \approx 5 \times 10^5$ in
wind tunnel tests \cite{Krogstad2012a}. Their turbine blades had an S826 profile
along their entire span, a profile chosen for its $Re$-independence. Walker et
al. \cite{Walker2014} similarly chose a NACA 63-618 foil for their axial-flow
turbine tests in a towing tank, which were performed at a mid span Reynolds
number $Re_c = 4 \times 10^5$. McTavish et al. \cite{McTavish2013} showed how
the near-wake expansion for an axial-flow rotor is increased at higher Reynolds
numbers, concluding that physical models should be designed with
$Re$-independence in mind if they are to be run at low $Re$.

\todo[inline]{Examples of very low $Re$ CFT work, e.g. Brochier et al.?}

@@

Previously, is has been observed experimentally that a high solidity cross-flow
turbine wake's unique vortical mean flow field is responsible for accelerated
wake recovery when compared with conventional axial-flow propeller-type turbines
\cite{Bachant2015-JoT}. In this study we seek to replicate the same momentum and
energy balance considerations at multiple Reynolds numbers, to examine the
implications on how small scale, i.e. low Reynolds number experiments may be
used to study flows in turbine arrays.
